\section{Milestone 2}\label{milestone-2}

\begin{itemize}
\item
  Interim Report
\item
  PDF mailed to aske@darpa.mil
\item
  Link to relevant documentation
\item
  Link to code
\item
  Report Contents
\item
  Definition of initial VDSOL for epidemic outbreak and response. Design
  VDSOL specification for initial domain based on published research,
  focus on models of H5N1 and H3N2 incidents and responses.
\item
  Design and development of initial AMIDOL Abstract Functional
  Interface. Specification of AFI primitives: state variables, actions,
  and predicates.
\item
  Initial AMIDOL machine-assisted inference engine development for
  prognostic queries on models defined in the VDSOL.
\item
  Investigation of epidemic response domain model. Implementation of
  Epidemic Response domain model for H5N1 and H3N2. Experiments on
  counter-factual analysis from models derived from these domains, and
  to build user stories on analysis, planning, and crisis response.
\item
  Definition of correctness, sensitivity, and uncertainty metrics.
  Communication of these results using the AFI to provide context in the
  ontology described by the VDSOL to improve practitioner understanding.
\end{itemize}

\subsection{Milestone 2 Report
Outline}\label{milestone-2-report-outline}

\begin{itemize}
\tightlist
\item
  VDSOL Definition
\item
  Generic language properties

  \begin{itemize}
  \tightlist
  \item
    Nouns
  \item
    Verbs
  \item
    Composability
  \item
    UI/UX Description
  \item
    JSON Export Language
  \end{itemize}
\item
  Epidemic VDSOL Toolbox
\item
  AMIDOL Abstract Intermediate Representation
\item
  State variables
\item
  Events
\item
  Input predicates
\item
  Output predicates
\item
  Representation
\item
  Inference Engine Targets
\item
  ODE
\item
  Numerical Solution
\item
  Simulation
\item
  Reward Variables and Reward Models
\item
  Rate reward variables
\item
  Impulse reward variables
\item
  Temporal Characteristics of Reward Variables
\item
  Translation of Reward Variables to IR
\item
  Expressions on Reward Variables
\item
  Design of Experiments and Results Database
\item
  Results Database
\item
  Prognostic Queries
\item
  Model Comparison
\item
  Design of Experiments
\item
  Counterfactual Exploration, Planning, Crisis Response
\item
  Correctness and Uncertainty
\item
  Communication of Results
\item
  Domain Models
\item
  SIS/SIRS
\item
  Stochiometry
\item
  HIV/Tat Model
\item
  Viral Infection Model
\item
  H5N1 Model
\item
  H3N2 Model
\item
  User Stories
\end{itemize}
